Measuring the Type Ia supernova delay time distribution via host galaxy rates in the Dark Energy Survey

### 2021-01-18 draft.tex

@@

    \item[v)]  objects must be covered by $ugrizJHK$ photometry, but do not require detections in all bands

@@

    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figs/SN_efficiencies.png}
    \caption{SN detection efficiencies split up by DES field. The $y-$axis represents the fraction of simulated SNe in a given redshift bin that would have been detected by DES-SN and passed light curve quality cuts.
    \label{fig:SN_efficiency}}
\end{figure}

@@

    \item[v)]  objects must be covered by $ugrizJHK$ photometry with either detections or upper limits

@@

    \item[viii)] galaxies must be brighter than $m_r \leq 24.5$, as this is the magnitude of the faintest SN host with a spectroscopic redshift.
